An Analysis of daily shelter and overnight service usage in Toronto focusing on shelter occupancy and capacity

### 2024-09-27 paper/paper.qmd
Final Revision of paper

# Appendix {#sec-appendix}
## Details of Data Cleaning
Occupancy date of 2021-2024 raw data are all transformed into date format for following new column of "year" mutation which represents the year of occupancy and capacity data that are collected. After the transformation, a combination work of these four raw dataset is done for more efficient following variables selection among all data. NAs are cleaned in categorical variable of overnight service type.

>>>>

# Appendix {#sec-app}
## Details of Data Cleaning
Occupancy date of 2021-2024 raw data are all transformed into date format for following new column of "year" mutation which represents the year of occupancy and capacity data that are collected. After the transformation, a combination work of these four raw dataset is done for more efficient following variables selection among all data. NAs are cleaned in categorical variable of overnight service type.
